Adaptive Resolution Simulation in Equilibrium and Beyond

### 2015-04-23 writeDown/pub.epj/paper.tex
rm color text

The time evolution of a classical molecular system
is modeled with Newtonian dynamics, and fundamental conservation laws
are satisfied, i.e.~the momentum and energy conservation.
However, in the AdResS system,
due to the spacial change of molecular resolution,
the two conservation laws cannot be satisfied at the same time~\cite{praprotnik2011comment,dellesite2007some}.
Traditionally, the AdResS scheme follows the \emph{force interpolation} approaches
that preserves the momentum conservation while breaking the energy
conservation.
Recently,
alternative approaches based on \emph{potential interpolation},
which preserve energy conservation while breaking the momentum conservation,
were designed~\cite{wang2013grand,potestio2013hamiltonian}.
The choice between the two AdResS branches therefore depends on the application. For example, in the
cases of studying hydrodynamics, the momentum conservation is preferred to the energy conservation.
However, if only the equilibrium properties are of interest,
the question should be asked on the ensemble that AdResS samples,
rather than directly on the mechanical conservation laws.
\recheck{It has been shown that, without the energy conservation, the force interpolation AdResS achieves
very high accuracy in equilibrium properties, such as the radial distribution function, the three-body correlation and the chemical potential~\cite{wang2013grand}.}
In this context,
it is worth noting that energy conservation is not a must for theoretical analyses on the equilibrium statistical properties,
although out of the energy conservation
one can define an auxiliary Hamiltonian~\cite{wang2013grand,agarwal2014chemical}
(not a physical one~\cite{dellesite2013multiscale}),
which reduces the mathematical difficulties.
In Sec.~\ref{sec:statistical} the force and potential interpolations are investigated 
under the same theoretical framework GC-AdResS (GC stands for ``Grand-Canonical like'')~\cite{wang2013grand} that raises necessary conditions
for a grand-canonical sampling with AdResS scheme.
In Sec.~\ref{sec:thermodynamic} the equilibrium thermodynamic relations between the resolutions are
provided for both branches of the AdResS.
From these relations, it is noticed that the absence of mechanical conservation laws 
modifies the way of thermodynamic equilibrium between the resolutions.

The GC-AdResS framework answers how to accurately compute the  equilibrium properties.
However, although the system is in equilibrium,
some properties, which are called dynamical properties,
\recheck{depend not only on the equilibrium ensemble, but also on the dynamics of the system.}
% cannot be simply computed from the equilibrium ensemble averages.
% These properties are called dynamical properties.
A typical example is the velocity auto-correlation\footnote{
  \recheck{
  The velocity auto-correlation
  % is the ensemble average
  % of the spontaneous fluctuation of the molecular velocity, being more precisly,
  is defined by the correlation between the velocity at a certain time and a time interval, e.g., $\Delta t$ later.
  It should be noted that
  the velocity auto-correlation depends on way that the system evolves in the time interval $\Delta t$,
  therefore, it is a dynamical property. }}.
% that describs the infiniesimal response of the system
% to external perturbation.
Moreover, the time-scales of conformational transformations
of bio-macromolecules (e.g.~protein and DNA)
are, again, dynamical properties.
The investigation of these  dynamical properties are out of the scope of the GC-AdResS framework and,
to the best of our knowledge, there is no theoretical answer on how accurately  AdResS reproduces the 
dynamical properties of a system.
Therefore, it is of practical significance to  provide numerical
evidence on the performance of AdResS in computing the dynamical properties.
In Sec.~\ref{sec:dynamical}, we investigate the
velocity auto-correlation in an AdResS water system, and the
leading relaxation time-scales and corresponding conformational dynamics of
a model dipeptide system.
The importance of designing the thermostat in these simulations
is also discussed.
The paper is closed by a concluding section
that mainly discusses the open problems in AdResS from both theoretical
and practical perspectives.

@@

In AdResS scheme, the simulation region $\Omega$ is 
decomposed without overlapping into three regions:
the atomistic region $\Omega_\AT$, the coarse-grained region $\Omega_\CG$, and
a hybrid region $\Omega_\HY$ bridging the former two regions.
That means the atomistic region is always connected to the coarse-grained region via a hybrid region.
The names of the atomistic and coarse-grained regions are self-explanatory, while
in the hybrid region each molecule has both the atomistic and coarse-grained resolutions.
A schematic plot of an AdResS simulation is presented in Fig.~\ref{fig:sys-region}.
AdResS uses a scalar weighting function $w(\vect r),\ \vect r\in\Omega$ 
to denote the resolution of the molecule at position $\vect r$.
% In the atomistic region the value of the
% weighting function is usually set to 1, while in the coarse-grained
% region it is usually set to 0. In between, there is a bybrid region
% that is denoted by $\Omega_\HY$
% (or called transition region), where the molecules
% has both the atomistic and coarse-grained resolutions, and the weighting function
% goes smoothly from 1 to 0.
The definition of the weighting function
is not unique, one possible and perhaps the most popular choice is
\begin{equation}\label{eqn:old-w}
  w(\vect r) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& \vect r \in \Omega_\AT\\
      &\cos^2\Big[\frac{\pi}{2 } \cdot \frac{\dist(\vect r, \Omega_\AT)}{d_\HY}\,\Big] && \vect r \in\Omega_\HY \\
      &0 &    & \vect r \in \Omega_\CG 
    \end{alignedat}
  \right.
\end{equation}
where $\dist(\vect r, \Omega_\AT)$ is the distance between the
position $\vect r$ and the atomistic region, which is defined
by $\dist(\vect r, \Omega_\AT) = \min_{\vect s\in\Omega_\AT} \vert
\vect r - \vect s \vert$.  $d_\HY$ is the thickness of the hybrid
region. We always assume the thickness of the hybrid region to be
uniform, which indicates that the weighting function smoothly vanishes
at the boundary between the hybrid and the coarse-grained regions.
AdResS requires 
all interactions\footnote{The long-range electrostatic interactions
  are also treated by the cut-off method. \recheck{It is possible by using e.g.~the Reaction-Field method~\cite{onsager1936electric,tironi1995generalized}
  to calculate the electrostatic interactions.}
} being treated
by the cut-off method\footnote{\recheck{AdResS uses the same general cut-off method as in normal MD simulations~\cite{frenkel2001understanding}.}}, and the thickness of
the hybrid region being at least one cut-off radius (denoted by $r_c$).
Moreover, owing to the double-resolution of hybrid molecules,
an atomistic molecule only interacts with the 
atomistic resolution of a hybrid molecule,
while a coarse-grained molecule only interacts with the coarse-grained resolution
of a hybrid molecule.
The atomistic molecules are thus not directly interacting with the coarse-grained molecules.
The benefit of these settings is that
there is no extra work for modeling the cross-scale interactions.

@@

The potential interpolation approach defines the hybrid energy by
\footnote{
\recheck{
  It worth noting that in Ref.~\cite{potestio2013hamiltonian} the potential interpolation is defined in a slightly different way:
  The product of the weighting functions $w_\moleidxone w_\moleidxtwo$ is replaced by the average average of them, i.e., $(w_\moleidxone + w_\moleidxtwo)/2$.}}
\begin{align}\label{eqn:v-v-interpol}
  {V}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{V}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){V}^{\CG}_{\moleidxone\moleidxtwo}.
\end{align}
The intermolecular force is therefore calculated by taking the negative gradient on the potential ${\vect F}^V_{\moleidxone \moleidxtwo}= -\nabla_{\moleidxone}{V}_{\moleidxone \moleidxtwo}$,
which is explicitly written as
\begin{align}\label{eqn:f-v-interpol}
  {\vect F}^V_{\moleidxone \moleidxtwo}
  &=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo}  - \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}
Where $\nabla w_\moleidxone$ is the gradient of the weighting function measured at position $\vect r_\moleidxone$,
and the superscript ``$V$'' denotes that the force is defined
by the potential interpolation.
By  definition~\eqref{eqn:f-v-interpol}, the force of the potential interpolation is conservative. 
The difference between the force and potential
interpolations lies in the last term  of Eq.~\eqref{eqn:f-v-interpol}, which is a force
acting along the direction of decreasing weighting function.
% This force is defined as \emph{the force of changing representation}.
It should be noted that
this force breaks the Newton's third law, therefore the force of potential interpolation
does not conserve the momentum.
We define the cumulative effect of this term by the \emph{force of changing representation}:
\begin{align}
  \vect F_\moleidxone^\rep = \sum_{\moleidxtwo}  \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}

@@

% \recheck{Remark, add the remark of inversed weighting function}
% \vskip .2cm
% \noindent\textbf{Remark}: In the case where the high-resolution simulation
% is extremely expensive, e.g.~the path-integral AdResS~\cite{poma2010classical},
% the extra cost for simulating with buffer region is therefore not desirable.
% One possible solution is to assign the value of weighting function in an reversed way:
% it taks 0 in high-resolution region, while takes 1 in low-resolution region.
% With the reversed weighting, the buffer region is on the coarse-grained side,

@@

In order to consider the accuracy of the AdResS from a statistical perspective, we always compare it with a full
atomistic reference system, which is of the same size as the AdResS system,
and contains the same number of molecules.
If the configuration of the atomistic region in AdResS 
is same as that of the corresponding subregion in the atomistic reference, then
AdResS is of good accuracy (see the comparison indicated by the red arrow in Fig.~\ref{fig:compare}).
A well-known conclusion of the standard statistical mechanics is that
when the reference system approximates the thermodynamic limit, the subsystem
\recheck{samples} the grand-canonical ensemble. Therefore, it is natural to investigate
if the atomistic region of AdResS also \recheck{samples} the grand-canonical ensemble
in the same thermodynamic limit. The theoretical framework presented in this section works for
both the force and potential interpolations.

% the atomistic region is embeded into the AdResS system as if it were embeded in to an atomistic environment,
% and the AdResS  is of good accuracy (see the red arrow in Fig.~\ref{fig:compare}).
% Here the corresponding atomistic region in the reference sys
% \recheck{comments on the ``atomistic region'' of the reference system}
\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figs/system.water/compare.eps}
  \caption{A schematic plot of the comparison between an AdResS system (left) and the full atomistic reference system (right).}
  \label{fig:compare}
\end{figure}

@@

The thermodynamic limit is taken in the sense that both the atomistic
and the coarse-grained regions are infinitely large, and at the same
time, the atomistic region is much smaller than the coarse-grained
region. The hybrid region is much smaller than both the atomistic and
coarse-grained regions.  Therefore, the volumes of the
three regions satisfies $V_\CG\gg V_\AT\gg V_\HY$.  The coarse-grained
region can be treated as an infinitely large particle and energy
reservoir for the atomistic region, and the hybrid region is an
infinitely thin filter that changes molecular resolution when a
molecule passes by. In the
thermodynamic limit, if there were no change of resolution (or
considering the full atomistic reference system), it is obvious that
the subregion corresponding to the atomistic region samples the
grand-canonical ensemble.  The question regarding the accuracy of
AdResS can be asked by: How accurately the atomistic region samples
the grand-canonical ensemble in the thermodynamic limit? More
specifically, we want to prove the probability density of the atomistic region satisfies
\begin{align}\label{eqn:dist-0}
  p(\vect x_\AT, N_\AT) \approx \frac{1}{\mathcal Z} \exp\Big\{{\beta\mu^\ast_\AT N_\AT - \beta \mh^\AT(\vect x_\AT)} \Big\}
\end{align}
where $\mu^\ast_\AT$ is the chemical potential of reference system in
the desired equilibrium, $\mathcal Z$ is the partition function
normalizing the probability density, $\mh^\AT$ is the \emph{atomistic}
Hamiltonian, \recheck{and $\beta$ denotes the inverse temperature $1/(k_BT)$.}
% defined in the the subregion of the reference system that
% corresponds to the atomistic region of the AdResS system.

@@

% In Sec.~\ref{sec:statistical}, we investigated the accuracy of AdResS
% in sampling the equilibrium ensemble.
In principle, all quantities that
can be written down in terms of equilibrium ensemble averages should
be computed with high accuracy when using an AdResS simulation that approximately samples the grand-canonical ensemble.
However, under this framework one has little knowledge regarding the quantities
that are \recheck{beyond equilibrium} ensemble averages.
For example, the non-equilibrium response of the system
with respect to an external perturbation, which is 
either computed by brute force non-equilibrium simulations~\cite{wang2014exploring}, or by
equilibrium time-correlation function via the Green-Kubo
relation~\cite{green1954markoff,kubo1957statistical} if the perturbation is small. The
time-correlation function, although measured in equilibrium
simulations, depends on how the dynamics
of the system is implemented.
The quantities of this type are called \emph{dynamical properties} of the system.
In principle, the Hamiltonian dynamics should be used to compute the dynamical properties,
however, due to the truncation error in computer simulations, it
is technically difficult to conserve the energy in very long MD simulations.
To this end thermostats are sometimes coupled to keep the system at desired thermodynamic
state.
It is worth noting that the thermostats are designed to sample equilibrium distributions, and 
disturb the Hamiltonian dynamics in an artificial way.
Therefore, when applying the thermostats
in computing the dynamical properties, the potential artifacts
should be checked carefully.
In the context of AdResS, we propose an alternative way of thermostating
the system, the local thermostat method~\cite{wang2014exploring},
which is proved to be free of the artifacts in computing the dynamical properties, in the following section.

@@

% \recheck{the difficulty of Langevin thermostat: destroy dynamics. Test local thermostating~\cite{wang2014exploring}
% }

@@

In the example of alanine dipeptide dissolved in water, the states in the MSM
is defined by uniformly dividing the $\phi$-$\psi$ space in to $20\times 20$ bins.
Each bin presents a state in MSM, and the transition matrix is sampled by equilibrium
MD simulations with the local thermostating scheme~\cite{wang2014exploring}.
The MSM is built and analyzed by the software EMMA~\cite{senne2012emma}.
The resulting eigenvalues and eigenvectors of AdResS are compared with the full atomistic reference under the same local thermostat in
Fig.~\ref{fig:ala-msm-t} and \ref{fig:ala-msm-v}. The
eigenvalues should be independent for sufficiently large $\tau$ if the MSM is of good
accuracy, and from Fig.~\ref{fig:ala-msm-t} they are so for $\tau \geq 20$~ps.
Also from the Fig.~\ref{fig:ala-msm-t}, the full atomistic
reference and the AdResS eigenvalues are consistent within the statistical
uncertainty.
From Fig.~\ref{fig:ala-msm-v}, the conformational transitions correspond
to $t_2$, $t_3$ and $t_4$ are $\{\confa \} \leftrightarrow \{\confc,\confd\}$,
$\{\confa, \confc \} \leftrightarrow \{\confb\}$ and $\{\confc \} \leftrightarrow \{\confd\}$, respectively.
The eigenvectors and the indicated conformational transitions of the AdResS are also consistent with
those of the full atomistic reference.
\recheck{
  The statistical uncertainty of estimating the longest non-trivial time-scale $t_2$ is higher than
  those of the shorter time-scales, because
  the transition $\{\confa \} \leftrightarrow \{\confc,\confd\}$ is less frequently sampled in
  an MD simulation than other transition events corresponding to shorter time-scales.
  Moreover, the fact that the equilibrium probability of being in states $\confc$ and $\confd$ is
  much less than that of being in state $\{\confa \}$ also leads to low frequency of the transition.
  % (This can be easily seen by, e.g., considering a simplified 2-state reversible Markov model).
  % Moreover, the
  % states $\confc$ and $\confd$ are less frequently visited, so the estimate of the  equilibrium probabilities of these
  % states are of lower accuracy, which also introduces larger statistical uncertainty
  % in estimating the implied time-scales of the transitions related to these states.
  The accuracy of estimating the 
  non-trivial time-scales may be improved by longer MD simulations, 
  or by deliberately choosing the initial states for MD runs~\cite{kohlhoff2014cloud}.}
Although calculated from the
equilibrium MD simulations, it should be noted that the leading time-scales and the
corresponding eigenvectors are not equilibrium properties, because
the transition probabilities (elements of the transition matrix) are actually
auto-correlation functions of the characteristic functions that are not \recheck{purely} equilibrium ensemble averages.

>>>>

The time evolution of a classical molecular system
is modeled with Newtonian dynamics, and fundamental conservation laws
are satisfied, i.e.~the momentum and energy conservation.
However, in the AdResS system,
due to the spacial change of molecular resolution,
the two conservation laws cannot be satisfied at the same time~\cite{praprotnik2011comment,dellesite2007some}.
Traditionally, the AdResS scheme follows the \emph{force interpolation} approaches
that preserves the momentum conservation while breaking the energy
conservation.
Recently,
alternative approaches based on \emph{potential interpolation},
which preserve energy conservation while breaking the momentum conservation,
were designed~\cite{wang2013grand,potestio2013hamiltonian}.
The choice between the two AdResS branches therefore depends on the application. For example, in the
cases of studying hydrodynamics, the momentum conservation is preferred to the energy conservation.
However, if only the equilibrium properties are of interest,
the question should be asked on the ensemble that AdResS samples,
rather than directly on the mechanical conservation laws.
{It has been shown that, without the energy conservation, the force interpolation AdResS achieves
very high accuracy in equilibrium properties, such as the radial distribution function, the three-body correlation and the chemical potential~\cite{wang2013grand}.}
In this context,
it is worth noting that energy conservation is not a must for theoretical analyses on the equilibrium statistical properties,
although out of the energy conservation
one can define an auxiliary Hamiltonian~\cite{wang2013grand,agarwal2014chemical}
(not a physical one~\cite{dellesite2013multiscale}),
which reduces the mathematical difficulties.
In Sec.~\ref{sec:statistical} the force and potential interpolations are investigated 
under the same theoretical framework GC-AdResS (GC stands for ``Grand-Canonical like'')~\cite{wang2013grand} that raises necessary conditions
for a grand-canonical sampling with AdResS scheme.
In Sec.~\ref{sec:thermodynamic} the equilibrium thermodynamic relations between the resolutions are
provided for both branches of the AdResS.
From these relations, it is noticed that the absence of mechanical conservation laws 
modifies the way of thermodynamic equilibrium between the resolutions.

The GC-AdResS framework answers how to accurately compute the  equilibrium properties.
However, although the system is in equilibrium,
some properties, which are called dynamical properties,
{depend not only on the equilibrium ensemble, but also on the dynamics of the system.}
% cannot be simply computed from the equilibrium ensemble averages.
% These properties are called dynamical properties.
A typical example is the velocity auto-correlation\footnote{
  {
  The velocity auto-correlation
  % is the ensemble average
  % of the spontaneous fluctuation of the molecular velocity, being more precisly,
  is defined by the correlation between the velocity at a certain time and a time interval, e.g., $\Delta t$ later.
  It should be noted that
  the velocity auto-correlation depends on way that the system evolves in the time interval $\Delta t$,
  therefore, it is a dynamical property. }}.
% that describs the infiniesimal response of the system
% to external perturbation.
Moreover, the time-scales of conformational transformations
of bio-macromolecules (e.g.~protein and DNA)
are, again, dynamical properties.
The investigation of these  dynamical properties are out of the scope of the GC-AdResS framework and,
to the best of our knowledge, there is no theoretical answer on how accurately  AdResS reproduces the 
dynamical properties of a system.
Therefore, it is of practical significance to  provide numerical
evidence on the performance of AdResS in computing the dynamical properties.
In Sec.~\ref{sec:dynamical}, we investigate the
velocity auto-correlation in an AdResS water system, and the
leading relaxation time-scales and corresponding conformational dynamics of
a model dipeptide system.
The importance of designing the thermostat in these simulations
is also discussed.
The paper is closed by a concluding section
that mainly discusses the open problems in AdResS from both theoretical
and practical perspectives.

@@

In AdResS scheme, the simulation region $\Omega$ is 
decomposed without overlapping into three regions:
the atomistic region $\Omega_\AT$, the coarse-grained region $\Omega_\CG$, and
a hybrid region $\Omega_\HY$ bridging the former two regions.
That means the atomistic region is always connected to the coarse-grained region via a hybrid region.
The names of the atomistic and coarse-grained regions are self-explanatory, while
in the hybrid region each molecule has both the atomistic and coarse-grained resolutions.
A schematic plot of an AdResS simulation is presented in Fig.~\ref{fig:sys-region}.
AdResS uses a scalar weighting function $w(\vect r),\ \vect r\in\Omega$ 
to denote the resolution of the molecule at position $\vect r$.
% In the atomistic region the value of the
% weighting function is usually set to 1, while in the coarse-grained
% region it is usually set to 0. In between, there is a bybrid region
% that is denoted by $\Omega_\HY$
% (or called transition region), where the molecules
% has both the atomistic and coarse-grained resolutions, and the weighting function
% goes smoothly from 1 to 0.
The definition of the weighting function
is not unique, one possible and perhaps the most popular choice is
\begin{equation}\label{eqn:old-w}
  w(\vect r) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& \vect r \in \Omega_\AT\\
      &\cos^2\Big[\frac{\pi}{2 } \cdot \frac{\dist(\vect r, \Omega_\AT)}{d_\HY}\,\Big] && \vect r \in\Omega_\HY \\
      &0 &    & \vect r \in \Omega_\CG 
    \end{alignedat}
  \right.
\end{equation}
where $\dist(\vect r, \Omega_\AT)$ is the distance between the
position $\vect r$ and the atomistic region, which is defined
by $\dist(\vect r, \Omega_\AT) = \min_{\vect s\in\Omega_\AT} \vert
\vect r - \vect s \vert$.  $d_\HY$ is the thickness of the hybrid
region. We always assume the thickness of the hybrid region to be
uniform, which indicates that the weighting function smoothly vanishes
at the boundary between the hybrid and the coarse-grained regions.
AdResS requires 
all interactions\footnote{The long-range electrostatic interactions
  are also treated by the cut-off method. {It is possible by using e.g.~the Reaction-Field method~\cite{onsager1936electric,tironi1995generalized}
  to calculate the electrostatic interactions.}
} being treated
by the cut-off method\footnote{{AdResS uses the same general cut-off method as in normal MD simulations~\cite{frenkel2001understanding}.}}, and the thickness of
the hybrid region being at least one cut-off radius (denoted by $r_c$).
Moreover, owing to the double-resolution of hybrid molecules,
an atomistic molecule only interacts with the 
atomistic resolution of a hybrid molecule,
while a coarse-grained molecule only interacts with the coarse-grained resolution
of a hybrid molecule.
The atomistic molecules are thus not directly interacting with the coarse-grained molecules.
The benefit of these settings is that
there is no extra work for modeling the cross-scale interactions.

@@

The potential interpolation approach defines the hybrid energy by
\footnote{
{
  It worth noting that in Ref.~\cite{potestio2013hamiltonian} the potential interpolation is defined in a slightly different way:
  The product of the weighting functions $w_\moleidxone w_\moleidxtwo$ is replaced by the average average of them, i.e., $(w_\moleidxone + w_\moleidxtwo)/2$.}}
\begin{align}\label{eqn:v-v-interpol}
  {V}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{V}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){V}^{\CG}_{\moleidxone\moleidxtwo}.
\end{align}
The intermolecular force is therefore calculated by taking the negative gradient on the potential ${\vect F}^V_{\moleidxone \moleidxtwo}= -\nabla_{\moleidxone}{V}_{\moleidxone \moleidxtwo}$,
which is explicitly written as
\begin{align}\label{eqn:f-v-interpol}
  {\vect F}^V_{\moleidxone \moleidxtwo}
  &=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo}  - \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}
Where $\nabla w_\moleidxone$ is the gradient of the weighting function measured at position $\vect r_\moleidxone$,
and the superscript ``$V$'' denotes that the force is defined
by the potential interpolation.
By  definition~\eqref{eqn:f-v-interpol}, the force of the potential interpolation is conservative. 
The difference between the force and potential
interpolations lies in the last term  of Eq.~\eqref{eqn:f-v-interpol}, which is a force
acting along the direction of decreasing weighting function.
% This force is defined as \emph{the force of changing representation}.
It should be noted that
this force breaks the Newton's third law, therefore the force of potential interpolation
does not conserve the momentum.
We define the cumulative effect of this term by the \emph{force of changing representation}:
\begin{align}
  \vect F_\moleidxone^\rep = \sum_{\moleidxtwo}  \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}

@@

% {Remark, add the remark of inversed weighting function}
% \vskip .2cm
% \noindent\textbf{Remark}: In the case where the high-resolution simulation
% is extremely expensive, e.g.~the path-integral AdResS~\cite{poma2010classical},
% the extra cost for simulating with buffer region is therefore not desirable.
% One possible solution is to assign the value of weighting function in an reversed way:
% it taks 0 in high-resolution region, while takes 1 in low-resolution region.
% With the reversed weighting, the buffer region is on the coarse-grained side,

@@

In order to consider the accuracy of the AdResS from a statistical perspective, we always compare it with a full
atomistic reference system, which is of the same size as the AdResS system,
and contains the same number of molecules.
If the configuration of the atomistic region in AdResS 
is same as that of the corresponding subregion in the atomistic reference, then
AdResS is of good accuracy (see the comparison indicated by the red arrow in Fig.~\ref{fig:compare}).
A well-known conclusion of the standard statistical mechanics is that
when the reference system approximates the thermodynamic limit, the subsystem
{samples} the grand-canonical ensemble. Therefore, it is natural to investigate
if the atomistic region of AdResS also {samples} the grand-canonical ensemble
in the same thermodynamic limit. The theoretical framework presented in this section works for
both the force and potential interpolations.

% the atomistic region is embeded into the AdResS system as if it were embeded in to an atomistic environment,
% and the AdResS  is of good accuracy (see the red arrow in Fig.~\ref{fig:compare}).
% Here the corresponding atomistic region in the reference sys
% {comments on the ``atomistic region'' of the reference system}
\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figs/system.water/compare.eps}
  \caption{A schematic plot of the comparison between an AdResS system (left) and the full atomistic reference system (right).}
  \label{fig:compare}
\end{figure}

@@

The thermodynamic limit is taken in the sense that both the atomistic
and the coarse-grained regions are infinitely large, and at the same
time, the atomistic region is much smaller than the coarse-grained
region. The hybrid region is much smaller than both the atomistic and
coarse-grained regions.  Therefore, the volumes of the
three regions satisfies $V_\CG\gg V_\AT\gg V_\HY$.  The coarse-grained
region can be treated as an infinitely large particle and energy
reservoir for the atomistic region, and the hybrid region is an
infinitely thin filter that changes molecular resolution when a
molecule passes by. In the
thermodynamic limit, if there were no change of resolution (or
considering the full atomistic reference system), it is obvious that
the subregion corresponding to the atomistic region samples the
grand-canonical ensemble.  The question regarding the accuracy of
AdResS can be asked by: How accurately the atomistic region samples
the grand-canonical ensemble in the thermodynamic limit? More
specifically, we want to prove the probability density of the atomistic region satisfies
\begin{align}\label{eqn:dist-0}
  p(\vect x_\AT, N_\AT) \approx \frac{1}{\mathcal Z} \exp\Big\{{\beta\mu^\ast_\AT N_\AT - \beta \mh^\AT(\vect x_\AT)} \Big\}
\end{align}
where $\mu^\ast_\AT$ is the chemical potential of reference system in
the desired equilibrium, $\mathcal Z$ is the partition function
normalizing the probability density, $\mh^\AT$ is the \emph{atomistic}
Hamiltonian, {and $\beta$ denotes the inverse temperature $1/(k_BT)$.}
% defined in the the subregion of the reference system that
% corresponds to the atomistic region of the AdResS system.

@@

% In Sec.~\ref{sec:statistical}, we investigated the accuracy of AdResS
% in sampling the equilibrium ensemble.
In principle, all quantities that
can be written down in terms of equilibrium ensemble averages should
be computed with high accuracy when using an AdResS simulation that approximately samples the grand-canonical ensemble.
However, under this framework one has little knowledge regarding the quantities
that are {beyond equilibrium} ensemble averages.
For example, the non-equilibrium response of the system
with respect to an external perturbation, which is 
either computed by brute force non-equilibrium simulations~\cite{wang2014exploring}, or by
equilibrium time-correlation function via the Green-Kubo
relation~\cite{green1954markoff,kubo1957statistical} if the perturbation is small. The
time-correlation function, although measured in equilibrium
simulations, depends on how the dynamics
of the system is implemented.
The quantities of this type are called \emph{dynamical properties} of the system.
In principle, the Hamiltonian dynamics should be used to compute the dynamical properties,
however, due to the truncation error in computer simulations, it
is technically difficult to conserve the energy in very long MD simulations.
To this end thermostats are sometimes coupled to keep the system at desired thermodynamic
state.
It is worth noting that the thermostats are designed to sample equilibrium distributions, and 
disturb the Hamiltonian dynamics in an artificial way.
Therefore, when applying the thermostats
in computing the dynamical properties, the potential artifacts
should be checked carefully.
In the context of AdResS, we propose an alternative way of thermostating
the system, the local thermostat method~\cite{wang2014exploring},
which is proved to be free of the artifacts in computing the dynamical properties, in the following section.

@@

% {the difficulty of Langevin thermostat: destroy dynamics. Test local thermostating~\cite{wang2014exploring}
% }

@@

In the example of alanine dipeptide dissolved in water, the states in the MSM
is defined by uniformly dividing the $\phi$-$\psi$ space in to $20\times 20$ bins.
Each bin presents a state in MSM, and the transition matrix is sampled by equilibrium
MD simulations with the local thermostating scheme~\cite{wang2014exploring}.
The MSM is built and analyzed by the software EMMA~\cite{senne2012emma}.
The resulting eigenvalues and eigenvectors of AdResS are compared with the full atomistic reference under the same local thermostat in
Fig.~\ref{fig:ala-msm-t} and \ref{fig:ala-msm-v}. The
eigenvalues should be independent for sufficiently large $\tau$ if the MSM is of good
accuracy, and from Fig.~\ref{fig:ala-msm-t} they are so for $\tau \geq 20$~ps.
Also from the Fig.~\ref{fig:ala-msm-t}, the full atomistic
reference and the AdResS eigenvalues are consistent within the statistical
uncertainty.
From Fig.~\ref{fig:ala-msm-v}, the conformational transitions correspond
to $t_2$, $t_3$ and $t_4$ are $\{\confa \} \leftrightarrow \{\confc,\confd\}$,
$\{\confa, \confc \} \leftrightarrow \{\confb\}$ and $\{\confc \} \leftrightarrow \{\confd\}$, respectively.
The eigenvectors and the indicated conformational transitions of the AdResS are also consistent with
those of the full atomistic reference.
{
  The statistical uncertainty of estimating the longest non-trivial time-scale $t_2$ is higher than
  those of the shorter time-scales, because
  the transition $\{\confa \} \leftrightarrow \{\confc,\confd\}$ is less frequently sampled in
  an MD simulation than other transition events corresponding to shorter time-scales.
  Moreover, the fact that the equilibrium probability of being in states $\confc$ and $\confd$ is
  much less than that of being in state $\{\confa \}$ also leads to low frequency of the transition.
  % (This can be easily seen by, e.g., considering a simplified 2-state reversible Markov model).
  % Moreover, the
  % states $\confc$ and $\confd$ are less frequently visited, so the estimate of the  equilibrium probabilities of these
  % states are of lower accuracy, which also introduces larger statistical uncertainty
  % in estimating the implied time-scales of the transitions related to these states.
  The accuracy of estimating the 
  non-trivial time-scales may be improved by longer MD simulations, 
  or by deliberately choosing the initial states for MD runs~\cite{kohlhoff2014cloud}.}
Although calculated from the
equilibrium MD simulations, it should be noted that the leading time-scales and the
corresponding eigenvectors are not equilibrium properties, because
the transition probabilities (elements of the transition matrix) are actually
auto-correlation functions of the characteristic functions that are not {purely} equilibrium ensemble averages.
